Phylogeographic inference with microtellite and SNPs

### 2019-07-16 code/rmarkdown/article.Rmd
new hyla data. sample codes corrected

Format: add journal title  \newline
Abstract word count: xx \newline
Main word count: xx  \newline
Number of references: xx  \newline
Number of figures: xx  \newline
Number of tables: xx  \newline
Number of text boxes: xx  \newline
Number of equations: xx  \newline
Keywords: microtellites, DArTseq, SNPs, neighbour joining, structure, phylogeography, Hyla molleri, Pelobates cultripes, Iberian Peninsula   \newline
Spelling: British English (en-GB)   \newline
\clearpage

@@

*Number of markers and bootstrap support*. The number of SNPs can affect the phylogeographic patterns inferred from RAD-seq data (Hodel et al. 2017). We evaluated the effect of the number of SNPs on the support of the tree reconstructions. We sampled random subsets of 20000, 10000, 5000, 3000, 1000, 500 and 200 loci from the SNP dataset of *P. cultripes*. This process was repeated 5 times to overcome possible biases on marker choice. On each of these 5 subsets we computed 200 bootstrapped trees as above. We calculated the bootstrap supports by counting the number of partitions of the NJ tree from the full dataset (see above, `r adegenet::nLoc(gen$dart_pelo)` loci) the were present in the 1000 bootstrapped trees. The number of loci was linearized applying a natural logarithm and its relation with the bootstrap support was evaluated with a linear model in R.

>>>>

Format: add journal title  \newline
Abstract word count: xx \newline
Main word count: xx  \newline
Number of references: xx  \newline
Number of figures: xx  \newline
Number of tables: xx  \newline
Number of text boxes: xx  \newline
Number of equations: xx  \newline
Keywords: microtellites, DArTseq, SNPs, neighbour joining, structure, phylogeography, *Hyla molleri*, *Pelobates cultripes*, Iberian Peninsula   \newline
Spelling: British English (en-GB)   \newline
\clearpage

@@

*Number of markers and bootstrap support*. The number of SNPs can affect the phylogeographic patterns inferred from RAD-seq data (Hodel et al. 2017). We evaluated the effect of the number of SNPs on the support of the tree reconstructions. We sampled random subsets of 20000, 10000, 5000, 3000, 1000, 500 and 200 loci from the SNP dataset of *P. cultripes*. This process was repeated 5 times to overcome possible biases on marker choice. On each of these 5 subsets we computed 200 bootstrapped trees as above. We calculated the bootstrap supports by counting the number of partitions of the NJ tree from the full dataset (see above, 33144 loci) the were present in the 1000 bootstrapped trees. The number of loci was linearized applying a natural logarithm and its relation with the bootstrap support was evaluated with a linear model in R.
